Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Adjust formatting

|              |         |            |          |
|--------------|---------|------------|----------|
|              | **Low** | **Medium** | **High** |
| Test samples | 1715    | 1587       | 1278     |
| Precision    | 0.622   | 0.507      | 0.664    |
| Recall       | 0.799   | 0.38       | 0.616    |
| F1           | 0.7     | 0.434      | 0.639    |

>>>>

|                  |         |            |          |
|------------------|---------|------------|----------|
|                  | **Low** | **Medium** | **High** |
| **Test samples** | 1715    | 1587       | 1278     |
| **Precision**    | 0.622   | 0.507      | 0.664    |
| **Recall**       | 0.799   | 0.38       | 0.616    |
| **F1**           | 0.7     | 0.434      | 0.639    |
